Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-08-28 analysis/paper/paper-doc.qmd
add credit authorship

>>>>

# CRediT authorship contribution statement
Gayoung Park: Conceptualization, Software, Validation, Formal analysis,  Methodology, Resources, Data curation,  Writing - original draft, Writing - Review & Editing, Visualization, Project administration.

Ben Marwick: Software, Validation, Formal analysis, Investigation, Writing - Review & Editing, Visualization, Supervision
